---
title: "Reproducible Research: Peer Assessment 1"
author: "Jan Tatham"
output: 
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data

* Load the required Libraries
```{r}
library(ggplot2)
library(lubridate)
```

* Download the dataset activity.csv, if it does not already exists
```{r}
# Check if Data folderdd exists
if(!dir.exists('./Data')) {
  dir.create('./Data')
}

# Check of activity.csv file exists in Data folder
if(file.exists("./Data/activity.csv") == FALSE) {
  fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
  download.file(fileUrl, destfile = "./Data/activity.zip", mode = "wb")
  unzip("./Data/activity.zip")
}

```

* Load the data (i.e. read.csv())
```{r}
# Load the dataset
activity <- read.csv("activity.csv", header = TRUE)
```

* Transform the data
```{r}
activity$date <- as.Date(activity$date, format = "%Y-%m-%d")

```

## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
